Replication of Gantman et al. 2024

### 2024-02-14 manuscript.qmd
typo fix

exlcuded_subjects <- c(exclude_for_fashion_twice_subjects, exclude_for_non_response_subjects, exclude_for_non_word_response_subjects)

behavioral_data_filtered <- behavioral_data %>%
  filter(!subject_id %in% exlcuded_subjects)
```

>>>>

excluded_subjects <- c(exclude_for_fashion_twice_subjects, exclude_for_non_response_subjects, exclude_for_non_word_response_subjects)

behavioral_data_filtered <- behavioral_data %>%
  filter(!subject_id %in% excluded_subjects)
```
